Principle of least action as a software development method

### 2023-11-30 latex/ms.tex
.

\author{Paschalis~Bizopoulos
\thanks{P. Bizopoulos is an Independent Researcher, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com}}

@@

PLA can be used throughout all software-related decisions:
\begin{enumerate}
	\item whether to use dependencies (e.g.\ libraries, frameworks) or implement a build-in solution
	\item whether to use standards or extend/restrict/ignore them
	\item whether to implement/drop a feature
	\item whether to use a tool (e.g.\ text editor, IDE)
\end{enumerate}

@@

@@

\section{Variable naming}
think prime-modifier-class naming scheme and how it relates to the action-as-information

@@

>>>>

\author{Paschalis~Bizopoulos
\thanks{P. Bizopoulos is an Independent Researcher, Thessaloniki, Greece e-mail: pbizop@gmail.com}}

@@

PLA can be used throughout all software-related decisions. For example:
\begin{enumerate}
	\item whether to use dependencies (e.g.\ libraries, frameworks) or implement a build-in solution
	\item whether to use standards or extend/restrict/ignore them
	\item whether to implement/drop a feature
	\item whether to use a development tool (e.g.\ text editor, IDE)
\end{enumerate}

@@

It starts with a user requirement.
Is it important?
If yes then, should it be solved with software?
If yes, then does it already exist?
If no, then can it programmed as a feature to an existing repo?
If no then create new repo.
If yes, then is it a new directory in the existing repo?
If yes then does it use an artifact of another repo?
If yes, then make it a parent directory of the another repo.
If no, then program the user requirement into the main.py.

@@

\section{Variable naming}
think prime-modifier-class naming scheme and how it relates to the action-as-information
\begin{itemize}
	\item Single-function repositories to a verb-noun naming convention.
	\item Multi-function repositories are appended with -tool.
	\item Research papers are a whole sentence.
	\item Repositories with URL are named as the URL\@.
\end{itemize}

@@

\section{Folder structure}
\begin{itemize}
	\item prm/: permanent data
	\item tmp/: temporary data
	\item main.py: code
	\item Dockerfile: code for the environment
	\item pyproject.toml: data for the environment
\end{itemize}
